What is happening on Twitter? Tweet analysis and student research projects

### 2020-05-30 Rmd/jse-special-issue-2020.Rmd
switched to using ASA citation style file

---
title: "What is happening on Twitter? Tweet analysis and student research projects"
author: "Frederick J. Boehm and Bret M. Hanlon"
date: "June 15, 2020"
params:
  lastmod: !r lubridate::now()
bibliography: jse.bib
csl: chicago-annotated-bibliography.csl
geometry: "left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm"
output: 
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: FALSE
    number_sections: TRUE
    includes:
      in_header: head.tex
  bookdown::word_document2:
    toc: FALSE
---

@@

```{bash, eval = FALSE, fig.cap = "Example Tweet JSON"}
{
  "created_at": "Thu Apr 06 15:24:15 +0000 2017",
  "id_str": "850006245121695744",
  "text": "1\/ Today we\u2019re sharing our vision for the future of the Twitter API platform!",
  "user": {
    "id": 2244994945,
    "name": "Twitter Dev",
    "screen_name": "TwitterDev",
    "location": "Internet",
    "url": "https:\/\/dev.twitter.com\/",
    "description": "Your official source for Twitter Platform news, updates & events. 
    Need technical help? Visit https:\/\/twittercommunity.com\/ \u2328\ufe0f 
    #TapIntoTwitter"
  },
  "place": {   
  },
  "entities": {
    "hashtags": [      
    ],
    "urls": [
      {
        "url": "https:\/\/t.co\/XweGngmxlP",
        "unwound": {
          "url": "https:\/\/cards.twitter.com\/cards\/18ce53wgo4h\/3xo1c",
          "title": "Building the Future of the Twitter API Platform"
        }
      }
    ],
    "user_mentions": [     
    ]
  }
}
```

>>>>

---
title: "What is happening on Twitter? Tweet analysis and student research projects"
author: "Frederick J. Boehm and Bret M. Hanlon"
date: "June 15, 2020"
params:
  lastmod: !r lubridate::now()
bibliography: jse.bib
csl: american-statistical-association.csl
geometry: "left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm"
output: 
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: FALSE
    number_sections: TRUE
    includes:
      in_header: head.tex
  bookdown::word_document2:
    toc: FALSE
---

@@

```{bash, eval = FALSE, fig.cap = "Example Tweet JSON", echo = TRUE}
{
  "created_at": "Thu Apr 06 15:24:15 +0000 2017",
  "id_str": "850006245121695744",
  "text": "1\/ Today we\u2019re sharing our vision for the future of the Twitter API platform!",
  "user": {
    "id": 2244994945,
    "name": "Twitter Dev",
    "screen_name": "TwitterDev",
    "location": "Internet",
    "url": "https:\/\/dev.twitter.com\/",
    "description": "Your official source for Twitter Platform news, updates & events. 
    Need technical help? Visit https:\/\/twittercommunity.com\/ \u2328\ufe0f 
    #TapIntoTwitter"
  },
  "place": {   
  },
  "entities": {
    "hashtags": [      
    ],
    "urls": [
      {
        "url": "https:\/\/t.co\/XweGngmxlP",
        "unwound": {
          "url": "https:\/\/cards.twitter.com\/cards\/18ce53wgo4h\/3xo1c",
          "title": "Building the Future of the Twitter API Platform"
        }
      }
    ],
    "user_mentions": [     
    ]
  }
}
```
